A Fundamental Measure Theory Functional for Hard-Sphere Contact Densities

### 2012-07-19 papers/contact/paper.tex
work on sphere.cpp, and make contact plots a tad nicer Tested everything on kipu.

\newcommand\sphereExplanation{ Blue curves describe the density of
  hard spheres.  Green curves describe the contact density averaged
  according to the point of contact.  Red curves describe the contact
  density as averaged according to the centers of the spheres that are
  touching.  In each case, solid lines correspond to the Monte Carlo
  simulation, and dashed lines of various sorts represent DFT model
  predictions.}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/contact-08-013}
  \caption{Density and contact densities of thirteen hard spheres in a
    spherical cavity with diameter 8. \sphereExplanation }
  \label{fig:sphere-8}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/contact-12-112}
  \caption{Density and contact densities of 112 hard spheres in a
    spherical cavity with diameter 12.  \sphereExplanation}
  \label{fig:sphere-12}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/contact-16-265}
  \caption{Density and contact densities of 265 hard spheres in a
    spherical cavity with diameter 16. \sphereExplanation}
  \label{fig:sphere-16}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/gnn-sphere-08-013}
  \caption{Correlation multiplied twice by density of 13 hard spheres in a
    spherical cavity with diameter 8.}
  \label{fig:gnn-sphere-08-013}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/gnn-sphere-12-112}
  \caption{Correlation multiplied twice by density of 112 hard spheres in a
    spherical cavity with diameter 12.}
  \label{fig:gnn-sphere-12-112}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/gnn-sphere-16-265}
  \caption{Correlation multiplied twice by density of 265 hard spheres in a
    spherical cavity with diameter 16.}
  \label{fig:gnn-sphere-16-265}
\end{figure}

@@

The next geometry we consider is a number of hard spheres confined
within a spherical cavity.  In
Figures~\ref{fig:sphere-8}-\ref{fig:sphere-16}, we show the densities
and contact densities for several cavity sizes \fixme{at a variety of
  filling fractions}.  We chose cavities that are large enough that
the center of the sphere is bulk-like, so that we can interpret the
behavior near the interface as behavior that should be typical of the
behavior of the hard sphere fluid near a concave surface.

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/inner-4-30}
  \caption{Density and contact densities around a hard sphere with
    radius 1.}
  \label{fig:inner-4-30}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/inner-4-40}
  \caption{Density and contact densities around a hard sphere with
    radius 1.}
  \label{fig:inner-4-40}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/inner-8-30}
  \caption{Density and contact densities around a hard sphere with
    radius 3.}
  \label{fig:inner-8-30}
\end{figure}

@@

>>>>

@@

The next geometry we consider is a number of hard spheres confined
within a spherical cavity.  In
Figures~\ref{fig:sphere-8}-\ref{fig:sphere-16}, we show the densities
and contact densities for several cavity sizes \fixme{at a variety of
  filling fractions}.  We chose cavities that are large enough that
the center of the sphere is bulk-like, so that we can interpret the
behavior near the interface as behavior that should be typical of the
behavior of the hard sphere fluid near a concave surface.
\begin{center}
  \includegraphics[width=\columnwidth]{figs/outer-16-05}
\end{center}
\begin{center}
  \includegraphics[width=\columnwidth]{figs/outer-16-04}
\end{center}
\begin{center}
  \includegraphics[width=\columnwidth]{figs/outer-16-03}
\end{center}

@@

\begin{center}
  \includegraphics[width=\columnwidth]{figs/inner-4-30}
\end{center}
\begin{center}
  \includegraphics[width=\columnwidth]{figs/inner-4-40}
\end{center}
\begin{center}
  \includegraphics[width=\columnwidth]{figs/inner-8-30}
\end{center}
